07-logistic_regression

### 2019-02-26 journals/07-logistic_regression/07-logistic_regression.Rmd
updates to journal 07

@@

### All Three Way Interactions

The code below fits a logistic regression model to the training data using the `train` function from the caret package. The nine features used to fit `rtrees` are included as main effects and with all two and three way interactions. The features are standardized prior to fitting the model using the `preProcess = "scale"` in `train`.

```{r}
# Fit or load the logistic regression model with all two and three way interactions
if(!file.exists("./data/logistic_inters3.rds")) {

  # Fit the model
  logistic_inters3 <- caret::train(as.factor(samesource) ~
                                       (ccf + rough_cor + D + sd_D + matches + 
                                          mismatches + cms + non_cms + sum_peaks)^3,
                                     preProcess = "scale",
                                     data = hamby173and252_train,
                                     method = "glm", 
                                     family = "binomial")

  # Save the model
  saveRDS(logistic_inters3, "./data/logistic_inters3.rds")

  # Load the model
  logistic_inters3 <- readRDS("./data/logistic_inters3.rds")

The output from this model is now shown.

@@

@@

```{r}
plot_features(lime_explain_mains$explain[1:12,])
```

```{r}
# Create or load the lime and explain objects for the two way interaction logisitic regression model
if(!file.exists("./data/lime_explain_inters2.rds")) {

  # Apply lime
  lime_inters2 <- lime(x = hamby173and252_train %>% select(rf_features), 
                       model = logistic_inters2)

  # Apply explain
  explain_inters2 <- explain(x = hamby224_test %>%
                               select(rf_features) %>% 
                               na.omit(), 
                             explainer = logistic_inters2_lime, 
                             n_labels = 1,
                             n_features = 3)

  # Join the lime and explain objects in a list
  lime_explain_inters2 <- list(lime = lime_inters2, explain = explain_inters2)

  # Save the lime and explain objects
  saveRDS(lime_explain_inters2, "./data/lime_explain_inters2.rds")

  # Load the lime and explain objects
  lime_explain_inters2 <- readRDS("./data/lime_explain_inters2.rds")

```{r}
plot_features(lime_explain_inters2$explain[1:12,])
```

### All Three Way Interactions

```{r}
# Create or load the lime and explain objects for the three way interaction logisitic regression model
if(!file.exists("./data/lime_explain_inters3.rds")) {

  # Apply lime
  lime_inters3 <- lime(x = hamby173and252_train %>% select(rf_features), 
                       model = logistic_inters3)

  # Apply explain
  explain_inters3 <- explain(x = hamby224_test %>%
                               select(rf_features) %>% 
                               na.omit(), 
                             explainer = logistic_inters3_lime, 
                             n_labels = 1,
                             n_features = 3)

  # Join the lime and explain objects in a list
  lime_explain_inters3 <- list(lime = lime_inters3, explain = explain_inters3)

  # Save the lime and explain objects
  saveRDS(lime_explain_inters3, "./data/lime_explain_inters3.rds")

  # Load the lime and explain objects
  lime_explain_inters3 <- readRDS("./data/lime_explain_inters3.rds")

```{r}
plot_features(lime_explain_inters3$explain[1:12,])
```

>>>>

}

summary(logistic_mains)
```

@@

@@

The results as computed by caret on the training data are shown below for the two logistic regression models. The accuracy shows that the models with two way interactions performs better on the training data.

```{r}
# Results from the models
data.frame(model = c("mains", "inters2")) %>%
  bind_cols(bind_rows(logistic_mains$results, logistic_inters2$results))
```

The AICs from the models are shown below. The model with two way interactions performs the best based on AIC.

```{r}
AIC(logistic_mains$finalModel)
AIC(logistic_inters2$finalModel)
```

I also wanted to know how the models perform on the test data. The models are used to make predictions on the test data and the MSEs are computed for each model. These are shown in the table below. The model with main effects only has the smallest MSE. I am guessing that the other model is overfitting the data.

```{r}
data.frame(mains = predict(logistic_mains, hamby224_test %>% select(rf_features)),
           inters2 = predict(logistic_inters2, hamby224_test %>% select(rf_features))) %>%
  summarise_at(vars(mains, inters2), 
               function(pred, obs) sum((as.logical(pred) - obs)^2) / n(),
               obs = hamby224_test %>% select(samesource) %>% na.omit())
```

@@

```{r}
plot_features(lime_explain_mains$explain[1:12,])
hamby224_test %>% filter(case == 1)
```
